---
title: "FML Assignment 2"
author: "Sai Kiran"
date: "2023-02-19"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(class)
library(dplyr)
library(caret)
library(tinytex)
ub=read.csv("C:/Users/panug/Downloads/UniversalBank.csv")
```

#eliminating unwanted columns like ID and Zip code
```{r}
ub$ID<-NULL
ub$ZIP.Code<-NULL
View(ub)
```
```{r}
#converting to a variable factor
ub$Personal.Loan=as.factor(ub$Personal.Loan)
```
#using is.na command to check if there are any NA values
```{r}
head(is.na(ub))
```
#transforming education into character
```{r}
ub$Education=as.character(ub$Education)
```
#Creating dummy  variables
```{r}
edu.1 <- ifelse(ub$Education==1 ,1,0)
edu.2 <- ifelse(ub$Education==2 ,1,0)
edu.3 <- ifelse(ub$Education==3 ,1,0)
ub.2<-data.frame(Age=ub$Age,Experience=ub$Experience,Income=ub$Income,Family=ub$Family,CCAvg=ub$CCAvg, education_1=edu.1,edu.2=edu.2,edu.3=edu.3,Personal.Loan=ub$Personal.Loan,Mortgage=ub$Mortgage,Securities.Account=ub$Securities.Account,CD.Account=ub$CD.Account,Online=ub$Online,CreditCard=ub$CreditCard)
```
#setting up testdata
```{r}
UB_test1<-data.frame(Age=40,Experience=10,Income=84,Family=2,CCAvg=2,edu.1=0,edu.2=1,edu.3=0,Mortgage=0,Securities.Account=0,CD.Account=0,Online=1,CreditCard=1)
```
#dividing data sets for training and testing
```{r}
set.seed(130)
ub.dummy<- createDataPartition(ub.2$Personal.Loan,p=.6,list=FALSE,times=1)
train1.ub <- ub.2[ub.dummy, ]
valid1.ub<- ub.2[-ub.dummy, ]
```
#Normalization
```{r}
ub.norm=preProcess(train1.ub[,-(6:9)],method=c("center","scale"))
trainNorm.ub =predict(ub.norm,train1.ub)
validNorm.ub =predict(ub.norm,valid1.ub)
testNorm.ub =predict(ub.norm,UB_test1)
View(trainNorm.ub)
```
#printing knn algorithm
```{r}
predicttrain.ub<-trainNorm.ub[,-9]
trainsample.ub<-trainNorm.ub[,9]
predictvalid.ub<-validNorm.ub[,-9]
validsample.ub<-validNorm.ub[,9]

predict.ub<-knn(predicttrain.ub, testNorm.ub, cl=trainsample.ub,k=1)
predict.ub

predict.uvb <- knn(predicttrain.ub, predictvalid.ub, cl=trainsample.ub, k=1)
```

#The loan proposal was turned down by the client. The decision is made when the k value is 0.

#printing out the best value of k
```{r}
set.seed(130)
grid.ub<-expand.grid(k=seq(1:30))                  
model.ub<-train(Personal.Loan~.,data=trainNorm.ub,method="knn",tuneGrid=grid.ub)
model.ub

value_k<-model.ub$bestTune[[1]]
```
#confusion matrix - validation dataset
```{r}
confusionMatrix(predict.uvb,validsample.ub)
```

#50:30:20 Repartition
```{r}
data_part_new <- createDataPartition(ub.2$Personal.Loan,p=0.5, list = F)
Train_new <- ub.2[data_part_new,]
Train_db_new <- ub.2[-data_part_new,]

data_part_new_1 <- createDataPartition(Train_db_new$Personal.Loan, p=0.6, list = F)
validate_new <- Train_db_new[data_part_new_1,]
test_new <- Train_db_new[-data_part_new_1,]
```
#Normalization
```{r}
norm_new <- preProcess(Train_new[,-(6:9)], method=c("center","scale"))
Train_new_p <- predict(norm_new, Train_new)
Validate_new_p <- predict(norm_new, validate_new)
Test_new_p <- predict(norm_new, test_new)
```
#predictors and labels
```{r}
train_pre <- Train_new_p[,-9]
validate_pre <- Validate_new_p[,-9]
test_pre <- Test_new_p[,-9]

train_l <- Train_new_p[,9]
validate_l <- Validate_new_p[,9]
test_l <- Test_new_p[,9]
```
#knn
```{r}
knn.t <- knn(train_pre,train_pre,cl= train_l, k=value_k)

knn.v <- knn(train_pre,validate_pre,cl=train_l, k=value_k)

knn.tes <- knn(train_pre,test_pre,cl=train_l, k=value_k)

confusionMatrix(knn.t,train_l)
confusionMatrix(knn.v,validate_l)
confusionMatrix(knn.tes,test_l)
```